Inferring disease architecture and predictive ability\\with LDpred2-auto

### 2022-10-10 paper/paper-infer.tex
finish README for code
export code

The UK Biobank data is available through a procedure described at \url{https://www.ukbiobank.ac.uk/using-the-resource/}. 
All code used for this paper is available at \url{https://github.com/privefl/paper-infer/tree/master/code} [TODO: UPDATE README].
Descriptions of UKBB phenotypes used here are available at \url{https://github.com/privefl/paper-infer/blob/main/phenotype-description.tsv}.
We have extensively used R packages bigstatsr and bigsnpr \cite[]{prive2017efficient} for analyzing large genetic data, packages from the future framework \cite[]{bengtsson2020unifying} for easy scheduling and parallelization of analyses on the HPC cluster, and packages from the tidyverse suite \cite[]{wickham2019welcome} for shaping and visualizing results.
The latest version of R package bigsnpr can be installed from GitHub.%, and a recent enough version can be installed from CRAN [TODO: VERIFY].

@@

\noindent[TODO: EXPORT LDREF FOR NEW HAPMAP3+]

\noindent[TODO: UPDATE LDPRED2 TUTORIAL TO INCLUDE INFERENCE]

>>>>

The UK Biobank data is available through a procedure described at \url{https://www.ukbiobank.ac.uk/using-the-resource/}. 
Descriptions of UK Biobank phenotypes used here are available at \url{https://github.com/privefl/paper-infer/blob/main/phenotype-description.tsv}.
LD matrices for HapMap3+ variants computed from the N.W. European UKBB data used in this paper are available at \url{https://doi.org/10.6084/m9.figshare.21305061}.
All code used for this paper is available at \url{https://github.com/privefl/paper-infer/tree/master/code}.
We have extensively used R packages bigstatsr and bigsnpr \cite[]{prive2017efficient} for analyzing large genetic data, packages from the future framework \cite[]{bengtsson2020unifying} for easy scheduling and parallelization of analyses on the HPC cluster, and packages from the tidyverse suite \cite[]{wickham2019welcome} for shaping and visualizing results.
The latest version of R package bigsnpr can be installed from GitHub.%, and a recent enough version can be installed from CRAN [TODO: VERIFY].

@@

%\noindent[TODO: EXPORT LDREF FOR NEW HAPMAP3+]

%\noindent[TODO: UPDATE LDPRED2 TUTORIAL TO INCLUDE INFERENCE]
